A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-22 manuscript.Rmd
fixed installation guide for macOS

A `Makefile` obeys a simple scheme. It contains a list of recipes. Each recipe has a target (the name of the recipe) followed by a colon and a list of dependent targets or files. If any of the dependencies have changed since the last time the target was built, the recipe's commands are executed to recreate the target file. We illustrate the use of Makefiles with an example. Assume the final product is a manuscript (`manuscript.pdf`). This manuscript is written in Rmarkdown (`manuscript.Rmd`) and includes dynamically generated plots from a raw data file (`data/iris.csv`) that needs to be preprocessed first using a separate script (`R/prepare_data.R`) into a prepared data file (`iris_prepped.csv`). A `Makefile` for these dependencies may look like this:

@@

data/iris_prepped.csv: R/prepare_data.R data/iris.csv
  Rscript -e 'source("R/prepare_data.R")'
```

The first line after the comment is the first (default) target called 'all', which depends on manuscript.pdf, which itself is a target. If Make is called without an argument, the first target is built. To create `manuscript.pdf` (the second target in the file), the file `manuscript.Rmd` needs to be rendered, which depends on `data/iris_prepped.csv`. This dependency is itself a target (the third target in the file). To create `data/iris_prepped.csv`, `R/prepare_data.R` and `data/iris.csv` are needed. If you type `make manuscript.pdf`, Make first checks whether the dependencies do exist and, if not, creates them. Here, if `data/iris_prepped.csv` does not exist, Make creates it by executing the third target. Also, if one of the dependencies of a target is newer than the target itself, Make updates everything that directly or indirectly depends on the target. Here, if `data\iris.csv` is newer than `data\ìris_prepped.csv`, Make will attempt to recreate `data\ìris_prepped.csv` first and then `manuscript.pdf`. If there is a dependency missing, and there is no target to make it, Make stops with an error message. It is a convention to have the first target named `all`, which creates the entire project. Subsequently, the command `make` without any argument automatically creates everything possible in the project. The button `Build All` from within RStudio triggers this process (see Figure \@ref(fig:buildpane-rstudio)).

@@

# install Docker via Homebrew
brew cask docker
```

>>>>

A `Makefile` obeys a simple scheme. It contains a list of recipes. Each recipe has a target (the name of the recipe) followed by a colon and a list of dependent targets or files. If any of the dependencies have changed since the last time the target was built, the recipe's commands are executed to recreate the target file. We illustrate the use of Makefiles with an example. Assume the final product is a manuscript (`manuscript.pdf`). This manuscript is written in Rmarkdown (`manuscript.Rmd`) and includes dynamically generated plots from a raw data file (`data/iris.csv`) that needs to be preprocessed first using a separate script (`R/prepare_data.R`) into a prepared data file (`ìris_prepped.csv`). A `Makefile` for these dependencies may look like this:

@@

data/ìris_prepped.csv: R/prepare_data.R data/iris.csv
  Rscript -e 'source("R/prepare_data.R")'
```

The first line after the comment is the first (default) target called 'all', which depends on manuscript.pdf, which itself is a target. If Make is called without an argument, the first target is built. To create `manuscript.pdf` (the second target in the file), the file `manuscript.Rmd` needs to be rendered, which depends on `data/ìris_prepped.csv`. This dependency is itself a target (the third target in the file). To create `data/ìris_prepped.csv`, `R/prepare_data.R` and `data/iris.csv` are needed. If you type `make manuscript.pdf`, Make first checks whether the dependencies do exist and, if not, creates them. Here, if `data/ìris_prepped.csv` does not exist, Make creates it by executing the third target. Also, if one of the dependencies of a target is newer than the target itself, Make updates everything that directly or indirectly depends on the target. Here, if `data\iris.csv` is newer than `data\ìris_prepped.csv`, Make will attempt to recreate `data\ìris_prepped.csv` first and then `manuscript.pdf`. If there is a dependency missing, and there is no target to make it, Make stops with an error message. It is a convention to have the first target named `all`, which creates the entire project. Subsequently, the command `make` without any argument automatically creates everything possible in the project. The button `Build All` from within RStudio triggers this process (see Figure \@ref(fig:buildpane-rstudio)).

@@

# install Docker via Homebrew
brew cask install docker
```
